Heatwaves Exacerbate Inequalities in Mental Health

### 2021-01-06 doc/temp-sentiment.tex
Updates from Overleaf

>>>>

\begin{figure}[H]
  \centering
  \includegraphics[width=\linewidth]{../res/wbgt-income.png}
  \caption{Change in sentiment across census block income groups as the Wet Bulb Globe Temperature increases.  For census blocks at the 5th percentile for income, even mild temperatures are associated with decreases in mood, while at higher temperatures, sentiment continues to decline.  For high-income census blocks at the 95th percentile, on the other hand, temperature must be quite high before a decrease in sentiment is observed.}
  \label{fig:wbgt-income}
\end{figure}
